Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-04-15 main/doc/building_scope.tex
documentation update

The class hierarchy is built if property \code{chord.scope.kind} has value \code{rta_reflect} or \code{cha}.
Users can control which classes are included in building the class hierarchy.
\Chord\ first constructs the entire classpath of the given program by concatenating in order the following
classpaths:

@@

All classes in the entire classpath (resulting from items 1--5 above) are included in the class hierarchy
with the following exceptions:
\begin{itemize}
\item
Duplicate classes, i.e., classes with the same name occurring in more than one classpath element;
in this case, all occurrences except the first are excluded. 
\item
All classes in \Chord's classpath are excluded, i.e., all classes in the classpath specified by property \code{chord.main.class.path},
such as those in packages and sub-packages of \code{chord}, \code{joeq}, \code{net.sf.bddbddb}, \code{net.sf.javabdd}, \code{javassist}, \code{gnu.trove}, \code{net.sf.saxon}, etc.
\item
If property \code{chord.ch.kind} has value \code{dynamic}, then \Chord\ runs the given program and
observes the set of all classes the JVM loads; any class not in this set is excluded.
By default, property \code{chord.ch.dynamic} has value \code{static}.
\item
If the superclass of a class $c$ is missing or if an interface implemented/extended by a class/interface
$c$ is missing, where ``missing" means that it is either not in the classpath resulting from items 1--5 above
or it is excluded by one of these rules, then $c$ itself is excluded.  Note that this rule is recursive, e.g.,
if $c$ has superclass $b$ which in turn has superclass $a$, and $a$ is missing, then both $b$ and $c$ are
excluded.
\end{itemize}

>>>>

The class hierarchy is built if property \code{chord.scope.kind} has value \code{rta_reflect} or \code{cha}.
Users can control which classes are included in building the class hierarchy by setting property \code{chord.ch.kind},
whose possible legal values are [\code{static}$|$\code{dynamic}].
\Chord\ first constructs the entire classpath of the given program by concatenating in order the following
classpaths:

@@

All classes in the entire classpath (resulting from items 1--5 above) are included in the class hierarchy
with the following exceptions:
\begin{itemize}
\item
Duplicate classes, i.e., classes with the same name occurring in more than one classpath element;
in this case, all occurrences except the first are excluded. 
\item
All classes in \Chord's classpath are excluded, i.e., all classes in the classpath specified by property \code{chord.main.class.path},
such as those in packages and sub-packages of \code{chord}, \code{joeq}, \code{net.sf.bddbddb}, \code{net.sf.javabdd}, \code{javassist}, \code{gnu.trove}, \code{net.sf.saxon}, etc.
\item
If property \code{chord.ch.kind} has value \code{dynamic}, then \Chord\ runs the given program and
observes the set of all classes the JVM loads; any class not in this set is excluded.
By default, property \code{chord.ch.kind} has value \code{static}.
\item
If the superclass of a class $c$ is missing or if an interface implemented/extended by a class/interface
$c$ is missing, where ``missing" means that it is either not in the classpath resulting from items 1--5 above
or it is excluded by one of these rules, then $c$ itself is excluded.  Note that this rule is recursive, e.g.,
if $c$ has superclass $b$ which in turn has superclass $a$, and $a$ is missing, then both $b$ and $c$ are
excluded.
\end{itemize}
